Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-06-05 src/docs_bioinference-poster/bioinference-poster.Rmd
Save exceedance probability output and put into poster #36

$$\\[0.1in]$$

@@

* For PCA-AGHQ $k = 3$ and $s = 8$ chosen using Scree plot to explain ~90% of variance
* For NUTS 4 chains of 100,000 thinned by 40 were required for good diagnostics
* Kolmogorov-Smirnov (KS) test based on the maximum difference between marginal ECDFs
  * Reduces average KS distance from 0.08 to 0.075
* Also considering joints via Pareto-smoothed importance sampling and maximum mean discrepancy
* Naomi can be used to assess probabilites targets have been met e.g. 90% of those who know their HIV status are on ART ("second 90")
  * Reduces RMSE for estimating second 90 exceedance probabilities by 10%

```{r}
# knitr::include_graphics("fig4.png")
# Figure of Second 90 here
```

@@

* Laplace marginals with matrix algebra approximations [@wood2020simplified] to speed up calculations
* Further methods for allocation of effort to "important" dimensions of hyperparameter grid

**Interested?** Working notebooks and R code available from `github.com/athowes/elgm-inf`. Or get in touch:

* `r fontawesome::fa("home", fill = "black")` `athowes.github.io`
* `r fontawesome::fa("envelope", fill = "black")` `ath19@ic.ac.uk`
* `r fontawesome::fa("twitter", fill = "black")` `adamhowes`

@@

@@

>>>>

@@

```{r echo=FALSE, message=FALSE, warning=FALSE}
ks <- readRDS("depends/ks_summary.rds")

ks_reduction <- ks %>%
  filter(Type == "Latent field") %>%
  summarise(
    ks_tmb = mean(`KS(TMB, tmbstan)`),
    ks_aghq = mean(`KS(aghq, tmbstan)`)
  ) %>%
  mutate(reduction = 100 * (ks_aghq - ks_tmb) / ks_tmb) %>%
  pull(reduction) %>%
  round()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
second90 <- readr::read_csv("depends/second90.csv")

second90_reduction <- second90 %>%
  summarise(
    rmse_tmb = 100 * sqrt(mean((tmbstan - TMB)^2)),
    rmse_aghq = 100 * sqrt(mean((tmbstan - aghq)^2))
  ) %>%
  mutate(reduction = 100 * (rmse_aghq - rmse_tmb) / rmse_tmb) %>%
  pull(reduction) %>%
  round()
```

* For PCA-AGHQ $k = 3$ and $s = 8$ chosen using Scree plot to explain ~90% of variance
* For NUTS 4 chains of 100,000 thinned by 40 were required for good diagnostics
* Kolmogorov-Smirnov (KS) test based on the maximum difference between marginal ECDFs
  * Average KS distance from NUTS reduced by `r abs(ks_reduction)`%
  * Also considering joint posteriors via Pareto-smoothed importance sampling and maximum mean discrepancy
* Naomi can be used to assess probabilities targets have been met e.g. 90% of those who know their HIV status are on ART ("second 90"). Both TMB and PCA-AGHQ have biased inferences (Figure \@ref(fig:fig4))
  * Reduced RMSE for estimating second 90 exceedance probabilities by `r abs(second90_reduction)`%

```{r fig4, echo=FALSE, fig.align='center', fig.cap='TMB is biased at estimating second 90 exceedance probabilities for women.'}
knitr::include_graphics("fig4.png")
```

@@

* **Can we do any better than modest improvements?**
* Laplace marginals with matrix algebra approximations [@wood2020simplified] to speed up calculations
* Further methods for allocation of effort to "important" dimensions of hyperparameter grid

@@

* `r fontawesome::fa("home", fill = "black")` `athowes.github.io`
* `r fontawesome::fa("envelope", fill = "black")` `ath19@ic.ac.uk`
* `r fontawesome::fa("twitter", fill = "black")` `@adamhowes`

@@

<!-- To-do: -->
<!-- * Add sex legend to Fig 4 -->
<!-- * Get "3. Inference procedure" to be on next page -->
<!-- * Try to reduce whitespace around Fig 3 -->
